Projecting Global Filesystems into Local Containers for High-throughput Computing on HPC Resources

### 2019-01-23 paper.tex
Updated figure layout

In the case of the simulation and analysis workloads at CERN,
unrestricted network access and FUSE support are critical for providing global filesystem access.
Nearly all research software used at CERN assumes the availability of the CernVM File System (CVMFS),
a distributed global filesystem built for distributing software and configuration data.
CMVFS provides a read-only, distributed file system using HTTP for network transport and extensive local
caching to rapidly distribute updates in software across the WLCG.
Dependence on CVMFS to distribute experiment software currently makes it impossible to take advantage of many HPC sites.
CVMFS requires unrestricted network access and is implemented as a FUSE module,
both of which sites often disallow for security and management reasons.

@@

As a result, it is difficult to contribute computational resources toward the LHC experiments without making some site-wide provisioning and configuration changes.
This is not an issue for the WLCG sites,
as they provide dedicated computing resources and can customize their setups to meet the requirements of CVMFS.
For a professor attempting to harness a campus cluster,
on the other hand, these requirements present a serious barrier.
Parrot, a debugging tool and personal filesystem developed at the University of Notre Dame,
can be used in cases where privilege on the worker nodes is limited and FUSE is not available but still requires unrestricted network access.
For computing at scale, it is important to provide a caching proxy as well,
which is likely to require assistance from administrators.

@@

With the rapidly increasing demands of the LHC experiments at CERN,
HPC resources are an appealing source of computing power to supplement the WLCG.
Leadership class machines such as Summit (?) will by themselves be able to perform a substantial portion of the work of the entire WLCG today.
Use of national-scale HPC resources across the United States and Europe such as XXX, YYY, Piz Daint at the Swiss CSCS HPC center could be key in meeting the computational demands following the LHC's high-luminosity upgrade.

@@

% https://indico.cern.ch/event/587955/contributions/2937411/attachments/1683156/2705423/WahidBhimji-CHEP18-NERSC.pdf
Another similar approach in use at NERSC is DVMFS.
Since creating static container images containing CVMFS is costly and difficult to customize,
DVMFS instead uses Cray DVS IO forwarders to mount a copy of CVMFS served over NFS.
This allows for less administrator involvement,
since the mirrored copy of CVMFS can be automatically updated on a regular basis.
After dealing with several implementation problems,
DVMFS is currently deployed at NERSC as an alternative to static images.
While this approach affords more flexibility in choice of repos and software versions,
it increases the job startup time and places additional requirements on the infrastructure.
To be usable in production, DVMFS requires a sufficient number of DVS servers to be provisioned.
DVMFS is nonetheless a viable solution as long as the costs of developing/maintaining the service and allocating infrastructure do not grow too high.

@@

\subsection{Creation of Specification}
File specifications can be created several ways,
with the obvious option being handwritten.
However, this quickly becomes unfeasible with
even a moderate number of requirements.
This leaves the need for an automate method to create
specifications.
The first method is to create a sample trace for your
jobs. 
Creating a trace from a sample job allows 
for a listing of actual files used, which
can be more accurate than handwritten listings.
As these jobs are typically on the order of thousands
to millions of jobs, sampling a small subset
can provide good software coverage with little
additional overhead. % the computation is still used
The burden of creating these traces is
dependant on the method used,
which could be an LD\_PRELOAD library,
using Parrot to track used files, % I think parrot was mentioned previously
or building the tracing in to the application.
As we will see later, we chose application
level tracing as it provides more context
for the use.

The second automated method is to use static
analysis for discover requirements.
This would allow the application to be analyzed
prior to running to determine what packages are
linked.
Static analysis can be done at several levels,
each providing different levels of control 
and flexibility.
This could be more language specific in the 
form of following import lines in python or
include lines in C.
The alternative is to use repository specific 
methods for setting up the environment,
such as bash scripts for pointing to correct 
software versions, or 
analyzing SCRAM\cite{DBLP:journals/corr/cs-OH-0306014} lines
to determine the configuration.
With either of these methods the issues
that arise come from bleeding edge or
experiment specific code that is not directly
handled by the configuration.
There is a significant mix between languages,
configurations methods, and software organization
practices even within a single repository,
which compounds the above issues in this method.

@@

For the analysis and creation pipeline discussed
later in the paper, tracing was used to provide
the file specifications. 
Tracings flexibility between repositories
and more precises file inclusion allow
for a lean package that provides coverage for
an experiment.

\subsection{Trace Sampling}
Tracing is attractive as it provides a consistent 
behavior between experiments and use cases.
In addition, it is easier to automate and sample arbitrary applications without assistance from each user.
This allows the solution to port between applications
quickly without having to delve in to the applications
specific configuration.
As previously mentioned, there are several methods for
obtaining a trace from a file.

Tracing was implemented in the CVMFS software and
interacts via the FUSE interface.
The tracing utility has been implemented in a way that 
minimizes the overhead if the tracer is deactivated and 
also minimizes the measurable overhead in the FUSE calls for an activated tracer 
by delegating the actual log writing to a separate thread to avoid blocks 
during the accesses to CVMFS. 
In fact, for a deactivated tracer the entire overhead consists of 
a single inline if for a subset of the FUSE calls.
This allows the actual observed CVMFS usage to  be tracked
and then used for determining the file specification.

@@

The use of a global revision number provides a quick reference
on the state of the repository at the highest level.
Global revision numbers can instantly verify the expected
contents, but does not give evidence of compatibility between
revisions.
As the revision number is global, any change to the repository
is reflected in a change to the revision number, which means 
some software is unchanged between revisions.
This method leaves much to be desired when using common stable
packages that change irregularly.

Aside from computing and checking the contents of the
repository or its files, it is possible to verify the
software using experiment computation.
This is a common method used to testing software
and works equally when the target software provides
coverage of the features used by the application.
The difficulty here is in providing tests that
behave consistently, verify if computation is
incorrect, and cover the desired features.
Though it is possible for the submitting user
to provide test with coverage, application
developers have a better grasp of it usage
and how to provide coverage in testing.
An additional method is to run the application
on a determined site for initial results and
compare in the future for verification, but
this relies on deterministic code which is 
not always the assumption in HEP computing.

\begin{table*}[t]
\begin{center}
\begin{tabular}{|c|r r r|r r r|}
\hline
CVMFS & & ls -lr & & & Shrinkwrap & \\
Repository & Total Size (MB) & inode Count & Time to walk & 
  Data Files & Deduplicated Data Files & Deduplicated Data (MB) \\ \hline
%alice-ocdb & 482,642,307,428 & 1,621,661 & 2:22 &
% 1,621,282 & 1,595 & 24,433,131,203\\
%alice & 3,980,875,747,986 & 27,322,350 & 51:53 & 
%  797,404 & 23,996,541 & 2,098,509,015,172\\
alice & 3,980,875 & 27,322,000 & 51:53 & 
  797,000 & 23,997,000 & 2,098,509\\
%atlas-condb & 719,548,941,240 & 11,781 & 0:04 &
%  10,940 & 229 & 471,492,086 \\
%atlas & 6,195,013,689,056 & 120,598,601 & 3:48:07 &
% 8,823,179 & 85,554,444 & 3,760,712,059,548 \\
atlas & 6,195,013 & 120,599,000 & 3:48:07 &
 8,823,000 & 85,554,000 & 3,760,712 \\
%boss & 120,048,527,315 & 2,418,025 & 4:18 &
% 256,061 & 1,868,192 & 72,301,955,666\\
boss & 120,048 & 2,418,000 & 4:18 &
 256,000 & 1,868,000 & 72,302\\
%cms & 581,789,406,847 & 26,224,567 & 1:07:30 &
% 18,667,178 & 101,448,867 & *2,242,658,825,701\\
cms & 581,789 & 26,225,000 & 1:07:30 &
 18,667,000 & 101,449,000 & *2,242,658\\
%geant4 & 297,571,283,648 & 7,128,024 & 10:36 &
% 323,280 & 6,219,891 & 68,381,969,660 \\
geant4 & 297,571 & 7,128,000 & 10:36 &
 323,000 & 6,220,000 & 68,382 \\
%grid & 30,642,826,259 & 714,235 & 1:17 &
% 141,622 & 583,923 & 18,804,003,040 \\
grid & 30,643 & 714,000 & 1:17 &
 142,000 & 584,000 & 18,804 \\
%lhcb & 2,134,893,079,440 & 33,736,802 & 1:01:26 &
% 10,032,339 & 20,406,235 & 368,070,277,634 \\
lhcb & 2,134,893 & 33,737,000 & 1:01:26 &
 10,032,000 & 20,406,000 & 368,070 \\
%na61 & 5,222,967,734 & 25,602 & 0:02 &
% 8,609 & 15,001 & 2,425,507,431 \\
na61 & 5,222 & 26,000 & 0:02 &
 9,000 & 15,000 & 2,426 \\
%sft & 3,996,527,275,237 & 128,608,792 & 4:17:58 &
% 6,821,699 & 63,210,139 & 2,016,609,810,573 \\ 
sft & 3,996,527 & 128,609,000 & 4:17:58 &
 6,822,000 & 63,210,000 & 2,016,610 \\ 
 \hline
\end{tabular}
\caption{CVMFS repository sizes.}
\label{tab:repo-sizes}
This table shows the size, number of inodes, and the amount
of duplicate data that is eliminated using CVMFS.
\end{center}
\end{table*}

\if 0
I AM NOT SURE WHICH WE WILL USE. WRAP THIS UP LATER.
\fi

@@

These methods were compared to showcase Shrinkwraps
behavior and evaluate usage performance.
The first analysis compares all three methods pulling 
an entire repository, to allow comparision between the
three.
GRAPH OF DEDUPLICATED DATA/FULL REPO SIZE/TIME TO CREATE.
The second looks at the time to update existing repositories 
between verison.
GRAPH UPDATE TIME ON FULL REPO AND MAYBE SUB REPO(SUB REPO ONLY COMPARES RSYNC AND SHRINKWRAP)
The third looks at hosting several projection at once and
switching between them.
COMPARES RSYNC AND SHRINKWRAP. UNCVMFS CANT COMPETE.

\begin{figure}[h]
\caption{COMPARISON OF SHRINKWRAP unCMVFS and RSYNC}
\label{figure:projection-comp}
\end{figure}

@@

All of the above methods describe utilize CVMFS
and rely on the internet connection to create
the projections.
A core assumption of this paper is that internet
access is limited at the compute nodes, so a method
is needed to transform and use these projections
for computation.
For this we looked at several methods for providing
these projections and compared using 
Container images (images specific to Docker, Singularity, ect.)
versus SquashFS images.
The goal is to find a flexible, compatible intermediate
format that allows projections to be moved between sites
and technologies.
For this purpose, Docker images, Singularity images, and 
SqaushFS are compared on their time to create,
storage requirements, and most importantly compatibility
with several used technologies, namely 
Docker, Singularity, and Shifter.

@@

When creating these images for analysis jobs its often the case that several
of these images may be created and used in the system.
Using Shrinkwrap to organize the repository data and projections,
the impact of an increasing number of images can be see in 
\Cref{figure:spec-size}.
This graph illustrates a new challenge that needs to be addressed.
As the number of experiments run and projections hosted by Shrinkwrap
increase. 
The raw number of images that need to be host increases to an unmanageable
size.
A solution is needed for how to manage these images and still
provide responsive execution of HEP analysis on HPC.

\subsection{Use Cases of Shrinkwrap}
%Here we illustrate several real world use cases.
%These use cases are being used as the existing solutions
%were not feasible and a new approach was needed.
%In analyzing these use cases we can see the beginnings of
%the problem outlined in the previous subsection.

@@

We are currently discussing options to integrate our shrinkwrap utility into the HPC deployment processes of ATLAS as we believe that the proposed software solution can help to reduce the overhead of HPC software delivery significantly. On the one hand the actual uncvmfs export process can be optimized as the current export workflow loads the entire CVMFS repository in a first step and later on removes certain files in the exported image which were not in fact needed. This is something that can be entirely avoided through the definition of exclusion rules passed to the shrinkwrap utility.

On the other hand, we believe that an export client which relies on the libcvmfs library might reduce the total overhead and therefore improve the export performance in comparison to both uncvmfs and rsync (for uncvmfs this is something that we haven’t had yet the chance to evaluate in an experiment).
As a longer-term goal, it might be useful to start tracing ATLAS simulation workflows on a few machines to collect data that might allow further export optimizations in a later stage through automated specification building.

@@

\begin{figure}
\includegraphics[width=\linewidth]{curated/cdf/cdf.pdf}
\label{fig:cdf}
\if 0
lots of small files
table shows duplication
long tail of large files
different scales, similar usage across repos

\begin{figure}
\includegraphics[width=\linewidth]{curated/closure/closure.pdf}
\label{fig:picks}
\if 0
you get more than you ask for
smaller requirements have relatively large responses
non-linear, so bigger ones have more duplicates
appraoches repo size in limit
merging is subject to drop-off(more duplication)
\fi
\end{figure}

@@

% explain alpha plot

@@

@@

@@

@@

These two limiting factors,
the compute and transfer cost in the highly merged case and the cache efficiency in the unmerged case,
serve as limits on the viable range of $\alpha$ values for the system.
Figure~\ref{fig:dist-eff} shows two vertical lines indicating these limits on a plot of efficiencies.
The left line shows a lower limit of around 30\% on the cache efficiency.
Choosing $\alpha$ too low results in cache efficiency reaching below 20\%.
On the right, the line gives an upper limit on the likelihood of merging.
As shown in Figure~\ref{fig:opcounts},
the amount of I/O and compute to update images becomes much larger if $\alpha$ is set too high.
These two limits define a range of viable values for $\alpha$.
There is no general rule for the placement of these limits,
wh depends strongly on the performance characteristics of the execution environment,
as well as the priorities of the administrators in optimizing the system.

\begin{figure}
\includegraphics[width=\linewidth]{curated/comparative/cache_efficiency.pdf}
justification for cache efficiency
unique vs total
full x range?
merging can give more unique data in less cache space
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{curated/comparative/container_efficiency.pdf}
\if 0
related to container efficiency: not exact but shows it
too much jitter from individual requests, so cumulative
crossover: hit rate allows reuse, so slightly less bytes written than requested
requested is based on random stream, constant
actual written goes up fast with alpha, so more overhead
proxy for compute/network/etc.
really steep at high alpha
\fi
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{curated/comparative/distribution_efficiency_comp.pdf}
\if 0
different data patterns cause different effects
random has high utilization
pushed right, limited opportunity for merge, since no overlap
merging doesn't help
random is not realistic though
merging is not general solution, but for trees of software, look at this

@@

\subsection{Quantifying Image Management Costs}

@@

We thus define the multiset $A$ as the union (with repetition) of all components in a set of requested images.
If multiple images request the same component,
it will occur multiple times in $A$.
The size required to store $A$,
including all duplicated elements,
is the storage space that would be required if a separate image were created for each job request.
$A$ captures the amount of (potentially) unnecessary duplication in the collection of images.
The initial approach described in section ?? would have a storage cost of $A$.
Note that it is always the case that $|C| \leq |A|$,
and if $|C| = |A|$ then there are no common components among the requested container images.
While large, full-repo images provide the best storage efficiency, being based solely on $|C|$,
they are expensive and unweildy to use in practice.
The initial approach in section ?? is extremely simple and friendly to use in practice,
but its storage cost is determined by $A$.
Our goal, therefore, in evaluating our improved image management scheme detailed in section ?? is to achieve storage cost as close to $C$ as possible without excessive overhead in terms of compute and network bandwidth to keep the image collection up to date.
We define \emph{cache efficiency} as $|C| / |A|$ to quantify the amount of duplication in the system cache.
With poor cache efficiency,
the available storage for the system cache is wasted on repeated copies of the same data.
Improving cache efficiency allows for more more unique image data within the same storage space,
or equivalently allows the same set of job requests to be served efficiently from a smaller cache.

\subsection{Effect of $\alpha$ Threshold}

\begin{figure*}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_cache_percent_plt.pdf}
\hfill
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_cache_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_request_percent_plt.pdf}
\hfill
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_request_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_uses_percent_plt.pdf}
\hfill
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_uses_percent_plt.pdf}
\if 0
[t] "just buy more cache"
efficiency is worse, since cache holds on to lots of questionable data
loads of opportunities to try merges, so we see a lot of unnecessary merges
less force removing bad choices, so more cruft can accumulate in many images
better cache utilization with tiny cache, but of course more thrashing
at scale, bad idea
large cache is too pricey at scale
[m] varying reuse doesn't affect too much
below 100 doesn't seem full/steady state yet
cache isn't settled? so haven't dropped bad merges; more unique data in cache boosts efficiency
[b] high number of requests, repeats don't matter
unique data dominates
hard to tell difference between [m] and [b], so not too sensitive to these
once you hit steady state, jobs count/repeats has little effect on efficiency
general trends of merging, not interesting by themselves
\fi
\end{figure*}

>>>>

In the case of the simulation and analysis workloads at CERN,
unrestricted network access and FUSE support are critical for providing global filesystem access.
Nearly all research software used at CERN assumes the availability of the CernVM File System (CVMFS),
a global filesystem built for distributing software and configuration data.
CMVFS provides a read-only, distributed file system using HTTP for network transport and extensive local
caching to rapidly distribute updates in software across the WLCG.
Dependence on CVMFS to distribute experiment software currently makes it impossible to take advantage of many HPC sites.
CVMFS requires unrestricted network access and is implemented as a FUSE module,
both of which sites often disallow for security and management reasons.

@@

As a result, it is difficult to contribute computational resources toward the LHC experiments without making some site-wide provisioning and configuration changes.
This is not an issue for the WLCG sites,
as they provide dedicated computing resources and can customize their setups to meet the requirements of CVMFS.
For a professor attempting to harness a campus cluster,
on the other hand, these requirements present a serious barrier.
Solutions exist such as
Parrot, a debugging tool and personal filesystem developed at the University of Notre Dame,
which sidesteps FUSE but still requires unrestricted network access and
UnCVMFS which locally store all of CVMFS to avoid network access, 
but relies on large storage and permission mounting.
For computing at scale, it is important to provide a caching proxy and concise storage,
which currently require assistance from administrators.

@@

With the rapidly increasing demands of the LHC experiments at CERN,
HPC resources are an appealing source of computing power to supplement the WLCG.
Leadership class machines such as Summit, at Oak Ridge National Laboratory, will by themselves be able to perform a substantial portion of the work of the entire WLCG today.
Use of national-scale HPC resources across the United States and Europe such as Cori at NERSC, Sierra at Lawrence Livermore National Laboratory, Piz Diant at Swiss National Supercomputing Centre could be key in meeting the computational demands following the LHC's high-luminosity upgrade.

@@

\if 0
% https://indico.cern.ch/event/587955/contributions/2937411/attachments/1683156/2705423/WahidBhimji-CHEP18-NERSC.pdf
Another similar approach in use at NERSC is DVMFS.
Since creating static container images containing CVMFS is costly and difficult to customize,
DVMFS instead uses Cray DVS IO forwarders to mount a copy of CVMFS served over NFS.
This allows for less administrator involvement,
since the mirrored copy of CVMFS can be automatically updated on a regular basis.
After dealing with several implementation problems,
DVMFS is currently deployed at NERSC as an alternative to static images.
While this approach affords more flexibility in choice of repos and software versions,
it increases the job startup time and places additional requirements on the infrastructure.
To be usable in production, DVMFS requires a sufficient number of DVS servers to be provisioned.
DVMFS is nonetheless a viable solution as long as the costs of developing/maintaining the service and allocating infrastructure do not grow too high.
\fi

@@

\subsection{Creation of Specification}
File specifications can be created several ways,
with the obvious option being handwritten.
However, this quickly becomes unfeasible with
even a moderate number of requirements.
This leaves the need for an automate method to create
specifications.

\subsubsection{Tracing}
The first method is to create a sample trace for your
jobs. 
Creating a trace from a sample job allows 
for a listing of actual files used, which
can be more accurate than handwritten listings.
As these jobs are typically on the order of thousands
to millions of jobs, sampling a small subset
can provide good software coverage with little
additional overhead. % the computation is still used
The burden of creating these traces is
dependant on the method used,
which could be an LD\_PRELOAD library,
using Parrot to track used files, % I think parrot was mentioned previously
or building the tracing in to the application.

Tracing is attractive as it provides a consistent 
behavior between experiments and use cases.
In addition, it is easier to automate and sample arbitrary applications without assistance from each user.
This allows the solution to port between applications
quickly without having to delve in to the applications
specific configuration.
As previously mentioned, there are several methods for
obtaining a trace from a file.

\begin{figure}
\includegraphics[width=\linewidth]{curated/cdf/cdf.pdf}
\caption{The distribution of file size for each repository.
From this we can see that the large majority of files
accumulate in the kilobyte to megabyte range.}
\label{fig:cdf}
\if 0
lots of small files
table shows duplication
long tail of large files
different scales, similar usage across repos

\subsubsection{Packages}
The second automated method is to use static
analysis for discover requirements.
This would allow the application to be analyzed
prior to running to determine what packages are
linked.
Static analysis can be done at several levels,
each providing different levels of control 
and flexibility.
This could be more language specific in the 
form of following import lines in python or
include lines in C.
The alternative is to use repository specific 
methods for setting up the environment,
such as bash scripts for pointing to correct 
software versions, or 
analyzing SCRAM\cite{DBLP:journals/corr/cs-OH-0306014} lines
to determine the configuration.
In the SFT CVMFS repository, where many core research packages are located,
dependencies are mapped for many packages using buildinfo files.
Chaining these buildinfo files together allow for a rough dependency
tree to be create, which was used to sample for \Cref{fig:picks}.
With either of these methods the issues
that arise come from bleeding edge or
experiment specific code that is not directly
handled by the configuration.
There is a significant mix between languages,
configurations methods, and software organization
practices even within a single repository,
which compounds the above issues in this method.

@@

\begin{figure}
\includegraphics[width=\linewidth]{curated/closure/closure.pdf}
\caption{Difference in number of packages and size when accounting for dependency based closure in selection.}
\label{fig:picks}
\if 0
you get more than you ask for
smaller requirements have relatively large responses
non-linear, so bigger ones have more duplicates
appraoches repo size in limit
merging is subject to drop-off(more duplication)
\fi
\end{figure}

@@

\begin{table*}[t]
\begin{center}
\begin{tabular}{|c|r r r|r r r|}
\hline
CVMFS & & ls -lr & & & Shrinkwrap & \\
Repository & Total Size (MB) & inode Count & Time to walk & 
  Data Files & Deduplicated Data Files & Deduplicated Data (MB) \\ \hline
%alice-ocdb & 482,642,307,428 & 1,621,661 & 2:22 &
% 1,621,282 & 1,595 & 24,433,131,203\\
%alice & 3,980,875,747,986 & 27,322,350 & 51:53 & 
%  797,404 & 23,996,541 & 2,098,509,015,172\\
alice & 3,980,875 & 27,322,000 & 51:53 & 
  797,000 & 23,997,000 & 2,098,509\\
%atlas-condb & 719,548,941,240 & 11,781 & 0:04 &
%  10,940 & 229 & 471,492,086 \\
%atlas & 6,195,013,689,056 & 120,598,601 & 3:48:07 &
% 8,823,179 & 85,554,444 & 3,760,712,059,548 \\
atlas & 6,195,013 & 120,599,000 & 3:48:07 &
 8,823,000 & 85,554,000 & 3,760,712 \\
%boss & 120,048,527,315 & 2,418,025 & 4:18 &
% 256,061 & 1,868,192 & 72,301,955,666\\
boss & 120,048 & 2,418,000 & 4:18 &
 256,000 & 1,868,000 & 72,302\\
%cms & 581,789,406,847 & 26,224,567 & 1:07:30 &
% 18,667,178 & 101,448,867 & *2,242,658,825,701\\
cms & 581,789 & 26,225,000 & 1:07:30 &
 18,667,000 & 101,449,000 & *2,242,658\\
%geant4 & 297,571,283,648 & 7,128,024 & 10:36 &
% 323,280 & 6,219,891 & 68,381,969,660 \\
geant4 & 297,571 & 7,128,000 & 10:36 &
 323,000 & 6,220,000 & 68,382 \\
%grid & 30,642,826,259 & 714,235 & 1:17 &
% 141,622 & 583,923 & 18,804,003,040 \\
grid & 30,643 & 714,000 & 1:17 &
 142,000 & 584,000 & 18,804 \\
%lhcb & 2,134,893,079,440 & 33,736,802 & 1:01:26 &
% 10,032,339 & 20,406,235 & 368,070,277,634 \\
lhcb & 2,134,893 & 33,737,000 & 1:01:26 &
 10,032,000 & 20,406,000 & 368,070 \\
%na61 & 5,222,967,734 & 25,602 & 0:02 &
% 8,609 & 15,001 & 2,425,507,431 \\
na61 & 5,222 & 26,000 & 0:02 &
 9,000 & 15,000 & 2,426 \\
%sft & 3,996,527,275,237 & 128,608,792 & 4:17:58 &
% 6,821,699 & 63,210,139 & 2,016,609,810,573 \\ 
sft & 3,996,527 & 128,609,000 & 4:17:58 &
 6,822,000 & 63,210,000 & 2,016,610 \\ 
 \hline
\end{tabular}
\caption{CVMFS repository sizes.}
\label{tab:repo-sizes}
This table shows the size, number of inodes (rounded to nearest thousand), and the amount
of duplicate data that is eliminated using CVMFS.
\end{center}
\end{table*}

@@

@@

All of the above methods described utilize CVMFS
and rely on the internet connection to create
the projections.
A core assumption is that external network
access is limited at the compute nodes, so a method
is needed to transform and use these projections
for computation.
For this several methods for providing
these projections using 
Container images (images specific to Docker, Singularity, ect.)
or SquashFS images can be used.
The goal is to find a flexible, compatible intermediate
format that allows projections to be moved between sites
and technologies.
For this purpose, Docker images, Singularity images, and 
SqaushFS are interchangeable as outputs of the Shrinkwrap process
and changed as needed for each use case as seen below.

%are compared on their time to create,
%storage requirements, and most importantly compatibility
%with several used technologies, namely 
%Docker, Singularity, and Shifter.

@@

@@

As previously described, NERSC is working in collaboration the LHC ATLAS project
to provide HPC resources for simulation and experimentation.
NERSC is currently deploying CVMFS images as monolithic container 
built using UnCVMFS, packaged in Squashfs images, and then containerized 
into Shifter or Singularity format, whose final format
relies on the target site.
This entire process can take up to a day to complete with the majority
of compute used to pull down and store the full CVMFS copy and storage
needs in excess of terabytes for images.
By combining either traced samples or statically defined requirements for 
jobs, Shrinkwrap can reduce these images orders of magnitudes.
Shrinkwrap which relies on the libcvmfs library reduces 
the total overhead and eliminates unnecessary files transfers
over UnCVMFS by allowing selections and rsync using data deduplication.

@@

@@

@@

Figure~\ref{fig:series} shows a single simulation of the image management system,
with $\alpha=0.0.75$, cache size XXX, ...
First, we note that most of the operations are merges.
This makes sense, as this simulation was at fairly high $\alpha$.
The total bytes written also closely tracks merges,
indicating that merging is the dominant source of I/O.
We can still see inserts over the course of the simulation.
At more extreme $\alpha$ values,
we would expect to see one of these operations almost exclusively.
As the data in cache continues to rise,
we eventually see the cache limit,
after which the delete count starts increasing.
Over the course of the simulation,
inserts and deletes are filling and emptying the cache such that it remains close to its storage limit.
We also observe the number of cache hits continue to rise despite deletions.
As we will see, merging allows for a greater proportion of hits even if the amount of data remains constant.
This is because frequently used data can be merged,
reducing duplication.
The cache limit then ensures that infrequently used parts are eventually removed.

@@

Since our simulation uses random simulated requests,
there is noticable variability between individual simulations.
Thus for a given choice of cache size, job count, etc.
we repeated the simulation 20 times and reported the median behavior over the runs.
At each choice of $\alpha$ (in steps of 0.05)
we performed a set of 20 simulated runs,
allowing us to plot various measurements of the system versus $\alpha$.

@@

\subsection{Determining a Viable Range for $\alpha$}

@@

These two limiting factors,
the compute and transfer cost in the highly merged case and the cache efficiency in the unmerged case,
serve as limits on the viable range of $\alpha$ values for the system.
Figure~\ref{fig:dist-eff} shows two vertical lines indicating these limits on a plot of efficiencies.
The left line shows a lower limit of around 30\% on the cache efficiency.
Choosing $\alpha$ too low results in cache efficiency reaching below 20\%.
On the right, the line gives an upper limit on the likelihood of merging.
As shown in Figure~\ref{fig:opcounts},
the amount of I/O and compute to update images becomes much larger if $\alpha$ is set too high.
These two limits define a range of viable values for $\alpha$.
There is no general rule for the placement of these limits,
which depends strongly on the performance characteristics of the execution environment,
as well as the priorities of the administrators in optimizing the system.
Rather than defining where these limits fall,
we give per-site considerations in choosing limits in Section ??.

\begin{figure}
\includegraphics[width=\linewidth]{curated/comparative/cache_efficiency.pdf}
\label{fig:cache-eff}
justification for cache efficiency
unique vs total
full x range?
merging can give more unique data in less cache space
\end{figure}

Figure~\ref{fig:cache-eff} shows the actual data sizes used to calculate the cache efficiency.
Without merging, the unique data makes up a small proportion of the cache.
With increased merging, the amount of unique data increases.
For sufficiently high $\alpha$,
merges occur more frequently than cache inserts,
resulting a drop in total storage size.
On the far right of Figure~\ref{fig:cache-eff},
the entire cache contents are merged into a single large image,
so that the unique and total data sizes become equal.
The cache efficiency metric is affected both by the increase in unique data and by the decrease in total cache size.

\begin{figure}
\includegraphics[width=\linewidth]{curated/comparative/container_efficiency.pdf}
\label{fig:container-eff}
\if 0
related to container efficiency: not exact but shows it
too much jitter from individual requests, so cumulative
crossover: hit rate allows reuse, so slightly less bytes written than requested
requested is based on random stream, constant
actual written goes up fast with alpha, so more overhead
proxy for compute/network/etc.
really steep at high alpha
\fi
\end{figure}

Figure~\ref{fig:container-eff} shows the cumulative costs of creating and updating images relative to the cost of simply providing the requested images.
These costs illustrate the effect of container efficiency over the course of a simulated run.
Without merging, the actual I/O and compute costs in the system closely follow the requests.
In Figure~\ref{fig:container-eff} the actual I/O is slightly smaller than the requested amount due to caching:
the system can sometimes reuse images without performing any I/O.
As $\alpha$ increases, the cost of updating and merging images comes to dominate the total cost.
Administrators migh decide, for example,
to spend at most twice the compute and I/O time relative to the the actual requested operations.
This would correspond to the upper compute limit shown on \label{fig:dist-eff}.
Depending on the priorities at a particular execution site,
either the storage utilization or compute and I/O time could be the critical factor in optimizing performance.

\begin{figure}
\includegraphics[width=\linewidth]{curated/comparative/distribution_efficiency_comp.pdf}
\label{fig:comp-eff}
\if 0
different data patterns cause different effects
random has high utilization
pushed right, limited opportunity for merge, since no overlap
merging doesn't help
random is not realistic though
merging is not general solution, but for trees of software, look at this

@@

We also compared the efficiencies of several types simulated images under a range of $\alpha$ values.
For the previous discussion, synthetic images were generated taking into account both the tree of package dependencies and usage statistics.
Figure~\ref{fig:comp-eff} shows a representative simulation with two other synthetic image types included.
First, we measured images considering only the dependency relationships but not usage.
These images show similar behavior to those previously discussed,
albeit with slightly lower efficiencies.
More realistic images primarily make the same trends more pronounced.
This suggests that even with random, non-realistic requests,
the tree structure of package dependencies is sufficient to produce duplication in the cache.
The other type of synthetic image shown in Figure~\ref{fig:comp-eff} is purely randomly generated.
The set of packages in each image was chosen uniformly randomly from the full SFT repo.
These random images do not take into account usage statistics or package dependencies,
making the software in them entirely nonfunctional.
For the random images,
we observe markedly different cache behavior.
The cache efficiency is much higher,
indicating a greater proportion of unique data in the cache.
Since the image contents were selected purely at random,
this is expected.
The container efficiency is also high over a much larger range of $\alpha$ values.
This is because there is effectively no merging until extremely high $\alpha$.
Since image contents are purely random,
there is no correlation between different images.
Thus, it is much more difficult to find images similar enough to merge until the $\alpha$ value is very lax.
This would indicate that our merging strategy is not applicable to arbitrary collections of data.
Random images show little to no effect for most $\alpha$ values.
Our merging strategy, which takes advantage of duplicated content included as a result of dependencies in software,
would be ill advised for situations that are not known to follow similar patterns of duplication.

\if 0
\subsection{Quantifying Image Management Costs}

@@

We thus define the multiset $A$ as the union (with repetition) of all components in a set of requested images.
If multiple images request the same component,
it will occur multiple times in $A$.
The size required to store $A$,
including all duplicated elements,
is the storage space that would be required if a separate image were created for each job request.
$A$ captures the amount of (potentially) unnecessary duplication in the collection of images.
The initial approach described in section ?? would have a storage cost of $A$.
Note that it is always the case that $|C| \leq |A|$,
and if $|C| = |A|$ then there are no common components among the requested container images.
While large, full-repo images provide the best storage efficiency, being based solely on $|C|$,
they are expensive and unweildy to use in practice.
The initial approach in section ?? is extremely simple and friendly to use in practice,
but its storage cost is determined by $A$.
Our goal, therefore, in evaluating our improved image management scheme detailed in section ?? is to achieve storage cost as close to $C$ as possible without excessive overhead in terms of compute and network bandwidth to keep the image collection up to date.
We define \emph{cache efficiency} as $|C| / |A|$ to quantify the amount of duplication in the system cache.
With poor cache efficiency,
the available storage for the system cache is wasted on repeated copies of the same data.
Improving cache efficiency allows for more more unique image data within the same storage space,
or equivalently allows the same set of job requests to be served efficiently from a smaller cache.
\fi

\subsection{System-specific Effects of $\alpha$ Threshold}

\begin{figure*}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_cache_percent_plt.pdf}
\hfill
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_cache_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_request_percent_plt.pdf}
\hfill
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_request_percent_plt.pdf}
\includegraphics[width=0.48\linewidth]{curated/sensitivity/container_efficiency_uses_percent_plt.pdf}
\hfill
\includegraphics[width=0.48\linewidth]{curated/sensitivity/cache_efficiency_uses_percent_plt.pdf}
\label{fig:sensitivity}
\if 0
[t] "just buy more cache"
efficiency is worse, since cache holds on to lots of questionable data
loads of opportunities to try merges, so we see a lot of unnecessary merges
less force removing bad choices, so more cruft can accumulate in many images
better cache utilization with tiny cache, but of course more thrashing
at scale, bad idea
large cache is too pricey at scale
[m] varying reuse doesn't affect too much
below 100 doesn't seem full/steady state yet
cache isn't settled? so haven't dropped bad merges; more unique data in cache boosts efficiency
[b] high number of requests, repeats don't matter
unique data dominates
hard to tell difference between [m] and [b], so not too sensitive to these
once you hit steady state, jobs count/repeats has little effect on efficiency
general trends of merging, not interesting by themselves
\fi
\end{figure*}
